\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-12-11 sections/chameleon.tex
Minor changes

This feature can be effective in resolving the problem that traditional tools tend to report errors that happened in source code from third-party libraries. With candidate expression cards, a programmer can freely change the context of the type error to the user-defined variables and functions to gain a better understanding of why her own code does not match the library code instead of the other direction.

@@

Programmers can use mouse and keyboard shortcuts to increment or decrement the step number or jump to any step. Typically, a programmer resolves  type errors by navigating through all the deduction steps and verifying whether each explanation aligns with the intended meaning of the program. Eventually, she will find a step that does not match her intention, and the type error can be fixed by modifying one of the two outlined error locations.

>>>>

This feature can be effective in resolving the problem that traditional tools tend to report errors that happened in source code from third-party libraries. With candidate expression cards, a programmer can freely change the context of the type error to the user-defined variables and functions to gain a better understanding of why their own code does not match the library code instead of the other direction.

@@

Programmers can use mouse and keyboard shortcuts to increment or decrement the step number or jump to any step. Typically, a programmer resolves  type errors by navigating through all the deduction steps and verifying whether each explanation aligns with the intended meaning of the program. Eventually, they will find a step that does not match her intention, and the type error can be fixed by modifying one of the two outlined error locations.
